Presentation Title

### 2017-08-21 thesis/formalities/preface.tex
Thanks Johan

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
Since early 2013, the time when I mined my first Bitcoin, 
I became cautious of the security and privacy issues surrounding centralised systems,
and became interested in building a decentralised society.
Following the Snowden revelations, the interest became a desire that has stayed with me ever since.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation, as well as my personal ambitions, led me to this thesis,
with the goal of creating a truly horizontally scalable solution.

>>>>

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
Since early 2013, the time when I mined my first Bitcoin, 
I became cautious of the security and privacy issues surrounding centralised systems
and became interested in building a decentralised society.
Following the Snowden revelations, the interest became a desire that has stayed with me ever since.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation, as well as my personal ambitions, led me to this thesis,
with the goal of creating a truly horizontally scalable solution.
